Chapter 3

### 2023-01-18 docs/chapter_03.qmd
fix data lineage diagram
update project timeline

```{mermaid}
graph TD
    A[Conflict event] -->|reporter| B(Online news article)
    B --> C

@@

    V --> |Our model| W(Our conflict predictions)

```

@@

```{mermaid}
gantt
    dateFormat  YYYY-MM-DD
    title       Capstone implementation timeline

    section Pre-capstone proposal
    Chapter 01            :done,    pre1, 2023-01-10,2023-01-12
    Chapter 02            :active,  pre2, 2023-01-17, 3d
    Chapter 03            :         pre3, 2023-01-19, 2d

    section Data
    Data ingestion pipelines            :datapipe, after pre3, 2023-01-23

    section Modelling
    Establish set of models             :active, m1, after pre3, 1w
    Establish model performance evaluation metrics :active, m2, after a1, 1w
    Implement model training pipelines  :modpipe, after pre3  , 2w
    Train model A                       :after modpipe, 1w
    Train model B                       :after modpipe, 1w
    Train model C                       :after modpipe, 1w
    Evaluate models                     :eval, after modpipe, 4w

    section Capstone paper
    Draft findings                      :draft, after eval, 2w
    Create figures                      :figs, after draft, 1w
    Copyediting and revision            :final, after figs, 2w
```

>>>>

```{mermaid}
graph TD
    A[Conflict event] -->|reporter| B(Online news article)
    B --> C(Scraped webpage)

@@

    V --> |Our model| W(Our conflict predictions)
```

@@

```{mermaid}
gantt
    dateFormat  YYYY-MM-DD
    title      Capstone project timeline

    section Project proposal
    Chapter 01            :done,    pre1, 2023-01-10,2023-01-12
    Chapter 02            :active,  pre2, 2023-01-17, 3d
    Chapter 03            :         pre3, 2023-01-19, 2d

    section Data
    Data ingestion pipelines                :datapipe, after pre3, 2023-01-23
    Training set and feature preparation    :after datapipe, 2023-02-05

    section Modelling
    Establish models and approaches to evaluate     :active, m1, after pre3, 1w
    Establish performance evaluation metrics        :active, m2, after a1, 1w
    Implement model training pipelines              :modpipe, after pre3  , 2w
    Train modeling approach A                       :train, after modpipe, 4w
    Train modeling approach B                       :train, after modpipe, 4w
    Train modeling approach C                       :train, after modpipe, 4w
    Evaluate models                                 :eval, after modpipe, 6w
    Train selected model(s)                         :model, after train, 3w

    section Capstone paper
    Draft findings                      :draft, after train, 2023-04-10
    Create figures                      :figs, after model, 2023-04-17
    Copyediting and revision            :final, after draft, 2023-05-04
    Presentation                        :pres, after final, 2023-05-11
```
